Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-12-07 paper/main.tex
Added disposition of results and discussion

\section{Python and Cython}
%What is it, how, why, alternatives?
% TODO: Finn en kilde på pythonting, om det trengs?
Python\footnote{\url{http://www.python.org/}} is a high-level general-purpose
programming language. Python is also an interpreted language, which means that
Python programs are compiled at runtime. There exists multiple implementations
of Python, however the most common, CPython, is implemented in C. The fact that
Python is a high-level language usually means that there are performance
penalties in contrast to lower level languages, such as C. To remedy this
problem it is possible to write extensions to the language by using the official
C-API. This approach has been used by several cryptographic libraries for
Python, such as pycryptopp\footnote{\url{http://tahoe-lafs.org/trac/pycryptopp}}
and the official hashlib\footnote{\url{http://code.krypto.org/python/hashlib/}}.

@@

\vspace{12pt}
Based on these criteria, we choose the fastest possible implementation based
on our benchmark in \ac{SUPERCOP}. The relative speed of each implementation, in
relation to other implementation for the same and other candidates are
available at source.
% TODO: Link to appendix with tahoe04 SUPERCOP results.

@@

\input{tables/sha3_implementations}
% FIXME: Insert image to visualize the forest of different implementations.

@@

\begin{itemize}
    \item Section should only contain the hard facts of our measurements
    \item What is tested and what is not tested?
    \item How much time is spent on hashing versus total time of
    uploading/downloading
    \item How much gain can Tahoe-LAFS get by switching to SHA-3?
\end{itemize}

\section{\ac{SUPERCOP} benchmarks}
The results of \ac{SHA}-3
256-bit functions and \ac{SHA}-256 benchmarking in \ac{SUPERCOP} can be seen in
tables \ref{tbl:supercop:long}, \ref{tbl:supercop:4096},
\ref{tbl:supercop:1536}, \ref{tbl:supercop:576}, \ref{tbl:supercop:64} and
\ref{tbl:supercop:8}. The lower the numbers, the faster the algorithms
performed in the test.

@@

@@

% TODO: Mention that some SUPERCOP candidates are missing UPDATE-functionality.
% What could have been done differently?
% Compare our results with general (supercop) results.
% Optimized candidates - which gain could be expected from more optimized
%   candidates?
% What if we had used another coding scheme? - does Cython lower the
%   candidates performance?
% Implications of only testing immutable files? (mutable files also
%   include directories)
% Adding a capability to support new hash functions in tahoe. (Our
%   current way breaks backwards compatability)
% Time gain of removing ``double'' SHA-256. Double only in digest()

>>>>

\section{Python and Cython}

Python\footnote{\url{http://www.python.org/}} is a high-level general-purpose
programming language. Python is also an interpreted language, which means that
Python programs are compiled at runtime. There exists multiple implementations
of Python, however the most common, CPython, is implemented in C. The fact that
Python is a high-level language usually means that there are performance
penalties in contrast to lower level languages, such as C. To remedy this
problem it is possible to write extensions to the language by using the official
C-API. This approach has been used by several cryptographic libraries for
Python, such as pycryptopp\footnote{\url{http://tahoe-lafs.org/trac/pycryptopp}}
and the official hashlib\footnote{\url{http://code.krypto.org/python/hashlib/}}.

@@

\vspace{12pt}
Based on these criteria, we choose the fastest possible implementation based
on our benchmark in \ac{SUPERCOP}. The relative speed of each implementation, in
relation to other implementation for the same and other candidates are
available at source.
% FIXME: Link to appendix with tahoe04 SUPERCOP results.

@@

\input{tables/sha3_implementations}

@@

% Munin?

% How much time is spent on hashing versus total time of
%   uploading/downloading

In this chapter, we will focus on the concrete results derived from our testing.

\section{Test scope}
% What is tested and what is not tested?
Immutable files are not tested, move text from Section 3.3.3.

\section{Measuring Performance}
Include code from hashutil.py and the use of time in bash.

\section{\ac{SUPERCOP} benchmarks}
% TODO: more introduction text here.

The results of \ac{SHA}-3 256-bit functions and \ac{SHA}-256 benchmarking in
\ac{SUPERCOP} can be seen in tables \ref{tbl:supercop:long},
\ref{tbl:supercop:4096}, \ref{tbl:supercop:1536}, \ref{tbl:supercop:576},
\ref{tbl:supercop:64} and \ref{tbl:supercop:8}. The lower the numbers, the
faster the algorithms performed in the test.

@@

\section{Results}

% Go graphs with plenty of short, descriptive comments.

@@

% This chapter should contain (in listed and grouped order):
% -----------------------------------------------------------
% Describe inconsitencies in the numbers, and try to explain them.
%
% Compare our results with general (supercop) results.
% Optimized candidates - which gain could be expected from more optimized
%   candidates?
% Mention that some SUPERCOP candidates are missing UPDATE-functionality.
%
% How much gain can Tahoe-LAFS get by switching to SHA-3?
% Time gain of removing ``double'' SHA-256. Double only in digest().
%
% Implications of only testing immutable files? (mutable files also
%   include directories)
% Adding a capability to support new hash functions in tahoe. (Our
%   current way breaks backwards compatability)
%
% What if we had used another coding scheme? - does Cython lower the
%   candidates performance?
%
% More general stuff. What could have been done differently?
